What if you drop that? Developmental changes in curiosity about physical interactions

### 2021-01-15 paper/paper2021.Rmd
minor edits

<!-- GK: possibly re-do this figure to have the proper orientations -->
```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
img <- png::readPNG("figs/fig1-objects.png")
grid::grid.raster(img)
```

@@

Participants were instructed that they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
Participants were then given a practice trial (see Figure 2), in which they were told that they should imagine dropping a given object (the torus) on each of two toys (the dumbbell or the pentagonal prism) in a bin. 
They were than asked to choose which toy to drop the torus on, and prompted to choose the most interesting or surprising combination.
After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
This was done to ensure that they understood the consequences of the choice they made.
After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on, but without videos.
Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (3-alternative forced choice).
The goal of the catch trials was to encourage participants to attend to the objects and the choices they made, and to exclude any participants who were incorrect on 2 or more of the catch trials.
Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants.

@@

```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
img <- png::readPNG("figs/online-child-practice-trial")
grid::grid.raster(img)
```

>>>>

<!-- GK: possibly re-do this figure to have the proper orientations -->
```{r fig3-child-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
img <- png::readPNG("figs/fig1-objects.png")
grid::grid.raster(img)
```

@@

Participants were instructed that they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
Participants were then given a practice trial (see Figure 2), in which they were told that they should imagine dropping a given object (the torus) on each of two toys (the dumbbell or the pentagonal prism) in a bin. 
They were then asked to choose which toy to drop the torus on, and prompted to choose the most interesting or surprising combination.
After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
This was done to ensure that they understood the consequences of the choice they made.
After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on, but without videos.
Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (3-alternative forced choice).
The goal of the catch trials was to encourage participants to attend to the objects and the choices they made, and to exclude any participants who were incorrect on 2 or more of the catch trials.
Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants.

@@

```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
img <- png::readPNG("figs/online-child-practice-trial.png")
grid::grid.raster(img)
```
